---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# metaSurvival

<!-- badges: start -->
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg)](https://opensource.org/licenses/MIT)
[![GitHub commit](https://img.shields.io/github/last-commit/shubhrampandey/metaSurvival)](https://github.com/shubhrampandey/metaSurvival/commit/master)
[![Travis build status](https://travis-ci.com/shubhrampandey/metaSurvival.svg?branch=master)](https://travis-ci.com/shubhrampandey/metaSurvival)
[![CRAN status](https://www.r-pkg.org/badges/version/metaSurvival)](https://CRAN.R-project.org/package=metaSurvival)
<!-- badges: end -->

The goal of metaSurvival is to ...

## Installation

You can install the released version of metaSurvival from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("metaSurvival")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("shubhrampandey/metaSurvival")
```
## Example

```{r setup}
library(metaSurvival)
```

First start with loading the example dataset.

```{r}
data(exampleData)
attach(exampleData)
head(exampleData)
```

Computation of summary survival with continuity correction.

```{r}
results<-msurv(Study, Time, NbRisk, Survival, confidence="Greenwood",correctionFlag = T,correctionVal = c(0.25,0.5))
results
```

Plot the estimates summary survival

```{r}
RandomEffectSummary<- results$summary.random

plot(Time, Survival, type="n", col="grey", ylim=c(0,1),xlab="Time",
 ylab="Survival")
 
for (i in unique(sort(Study))){
lines(Time[Study==i], Survival[Study==i], type="l", col="grey")
points(max(Time[Study==i]),
 Survival[Study==i & Time==max(Time[Study==i])], pch=15)
}

lines(RandomEffectSummary[,1], RandomEffectSummary[,2], type="l",
 col="red", lwd=3)
points(RandomEffectSummary[,1], RandomEffectSummary[,3], type="l",
 col="red", lty=3, lwd=3)
points(RandomEffectSummary[,1], RandomEffectSummary[,4], type="l",
 col="red", lty=3, lwd=3)
```

Computation of summary survival without continuity correction.

```{r}
results<-msurv(Study, Time, NbRisk, Survival, confidence="Greenwood",correctionFlag = F)
results
```

Plot the estimates summary survival

```{r}
RandomEffectSummary<- results$summary.random

plot(Time, Survival, type="n", col="grey", ylim=c(0,1),xlab="Time",
 ylab="Survival")
 
for (i in unique(sort(Study))){
lines(Time[Study==i], Survival[Study==i], type="l", col="grey")
points(max(Time[Study==i]),
 Survival[Study==i & Time==max(Time[Study==i])], pch=15)
}

lines(RandomEffectSummary[,1], RandomEffectSummary[,2], type="l",
 col="red", lwd=3)
points(RandomEffectSummary[,1], RandomEffectSummary[,3], type="l",
 col="red", lty=3, lwd=3)
points(RandomEffectSummary[,1], RandomEffectSummary[,4], type="l",
 col="red", lty=3, lwd=3)
```
